{\large BIBLIOGRAFIA:}

Roughgarden, Tim. \textit{Algorithms Illuminated (Part 2): Graph Algorithms and Data Structures}, Soundlikeyourself, 2018. 

\vspace{1cm}

{\large REFERÈNCIES:}

[1] “Sections and chapters.” Consulta 1 d’abril 2022. \url{https://es.overleaf.com/learn/latex/Sections_and_chapters}

[2] Admin. “Your Guide to Fancy Chapters in LaTeX.” LaTeX-Tutorial.Com (blog). Consulta 12 d’abril 2022. \url{https://latex-tutorial.com/fancy-chapters-latex/}

[3] TeX - LaTeX Stack Exchange. “Glenn Fncychap + Color of the Box.” Consulta 13 d’abril 2022. \url{https://tex.stackexchange.com/questions/405297/glenn-fncychap-color-of- \\ the-box} 

[4] “Using Colours in LaTeX.” Consulta 13 d’abril 2022. \url{https://www.overleaf.com/learn/latex/Using_colours_in_LaTeX}

[5] “¿Qué Es Un Algoritmo y Qué Es Un Programa?” Consulta 18 de juny 2022. \url{http://www.edu4java.com/es/conceptos/que-es-un-algoritmo-que-es-un-programa.html}

[6] “Lista Completa de Símbolos En LaTeX | Manualdelatex.Com.” Consulta 18 de juny 2022. \url{https://manualdelatex.com/simbolos#chapter8}

[7] --“ZoteroBib: Fast, Free Bibliography Generator - MLA, APA, Chicago, Harvard Citations.” Consulta 18 de juny 2022.   \url{https://zbib.org/#}

[8] ¿Qué Es Eso Del Problema P versus NP? Consulta 22 de juny 2022. \url{https://www.youtube.com/watch?v=UR2oDYZ-Sao}

[9] freeCodeCamp.org. “Beginners Guide to Big O Notation,”. Consulta 23 de juny 2022. \url{https://www.freecodecamp.org/news/my-first-foray-into-technology-c5b6e83fe8f1/}

[10] Mejia, Adrian. “How to Find Time Complexity of an Algorithm?“ Adrian Mejia Blog. Consulta 23 de juny 2022. \href{https://adrianmejia.com/how-to-find-time-complexity-of-an-algorithm-code-big-o-notation/}{\nolinkurl{https://adrianmejia.com/how-to-find-time-complexity-of-an- \\ algorithm-code-big-o-notation/}}

[11] Roura, Salvador. “Eficiència d’algorismes”. UPC. Consulta 23 de juny 2022. \url{https://www.cs.upc.edu/~roura/eficiencia.pdf}

[12] Big O Notation - Full Course. Consulta 6 de juliol 2022. \url{https://www.youtube.com/watch?v=Mo4vesaut8g}

[13] arvindpdmn, dineshpathak. “Algorithmic Complexity.” Consulta 7 de juliol 2022. \url{https://devopedia.org/algorithmic-complexity}

[14] “Real-World Example of Exponential Time Complexity.” Forum post. Stack Overflow, Consulta 7 de juliol 2022. \url{https://stackoverflow.com/q/7055652}

[15] Lovett, Pamela. “Big-O Notation: A Simple Explanation with Examples.” Consulta 7 de juliol 2022. \href{https://betterprogramming.pub/big-o-notation-a-simple-explanation-with-examples-a56347d1daca}{\nolinkurl{https://betterprogramming.pub/big-o-notation-a-simple-explanation- \\ with-examples-a56347d1daca}}

[16] “Hide an Entry from Toc in Latex.” Forum post. Stack Overflow. Consulta 12 de juliol 2022. \url{https://stackoverflow.com/q/2785260}

[17] Alraja, Humam Abo. “Logarithms \& Exponents in Complexity Analysis.” Consulta 15 de juliol 2022.
\href{https://towardsdatascience.com/logarithms-exponents-in-complexity-analysis-b8071979e847}{https://towardsdatascience.com/logarithms-exponents-in-complexity-analysis-b8071979e847}

[18] MIT. “Big O notation”.  Consulta 24 de juliol 2022. \url{https://web.mit.edu/16.070/www/lecture/big_o.pdf}

[19] GeeksforGeeks. “Bubble Sort Algorithm,” Consulta 24 de juliol 2022. \url{https://www.geeksforgeeks.org/bubble-sort/}

[20] LaTeX-Tutorial.com. “How to Make Clickable Links in LaTeX.” Consulta 27 de juliol 2022. \url{https://latex-tutorial.com/tutorials/hyperlinks/}

[21] Ljosa, Vebjorn. “Remove Ugly Borders around Clickable Cross-References and Hyperlinks.” Forum post. TeX - LaTeX Stack Exchange, April 13, 2017.  Consulta 27 de juliol 2022. \url{https://tex.stackexchange.com/q/823}

[22] MrD. “Answer to ‘How to Allow Line Break in a Long Hyperlink in a PDF Compiled by Latex-Dvips-Ps2pdf?’” TeX - LaTeX Stack Exchange, April 10, 2013. Consulta 27 de juliol 2022. \url{https://tex.stackexchange.com/a/108003}

[23] user133284. “Pagebreak for Minted in Figure.” Forum post. TeX - LaTeX Stack Exchange, May 9, 2017. Consulta 27 de juliol 2022.  \url{https://tex.stackexchange.com/q/368864}

[24] Simplilearn.com. “What Is DFS (Depth-First Search): Types, Complexity \& More | Simplilearn.” Consulta 26 d'agost 2022. 
\href{https://www.simplilearn.com/tutorials/data-structure-tutorial/dfs-algorithm}{https://www.simplilearn.com/tutorials/data-structure-tutorial/dfs-algorithm}

[25] “Example; Undirected and Unweighted Edges - C\# Data Structures and Algorithms [Book].” Consulta 28 d'agost 2022. \url{ https://www.oreilly.com/library/view/c-data-structures/9781788833738/0309b525-cfe4-429d-bdb9-53b25f94bbcd.xhtml}

[26] Quora. “Who Uses TeX, besides LaTeX?” Consulta 29 d'agost 2022. \url{https://www.quora.com/Who-uses-TeX-besides-LaTeX}

[27] Ivorra, Carlos. “Introducción al LATEX”. Consulta 29 d'agost 2022. \url{https://www.uv.es/~ivorra/Latex/LaTeX.pdf}